Dark Control: The Default Mode Network as a Reinforcement Learning Agent

### 2018-08-08 paper/paper.tex
more refs required rev2

Mental scenes created by neurological patients with HC lesion exposed a lack of
spatial integrity, richness in detail, and overall coherence.
%
Single-cell recordings in the animal HC revealed
constantly active neuronal populations whose firing coincided with
specific locations in space during environmental navigation.
Indeed, when an animal is choosing between alternative
paths, the corresponding neuronal populations in the HC
spike one after another  \citep{johnson2007neural}.
Such neuronal patterns in the HC appear to directly indicate upcoming behavior,
such as in planning navigational trajectories
\citep{pfeiffer2013hippocampal} and
memory consolidation of choice relevance \citep{lavilleon2015}.
Congruently,
London taxi drivers, humans with high performance in forecasting spatial navigation,
were shown to exhibit increased gray-matter volume in the
HC \citep{maguire2000navigation}.

>>>>

Mental scenes created by neurological patients with HC lesion exposed a lack of
spatial integrity, richness in detail, and overall coherence (c.f ~\citep{hassabis2007patients}).
%
Single-cell recordings in the animal HC revealed
constantly active neuronal populations whose firing coincided with
specific locations in space during environmental navigation.
Indeed, when an animal is choosing between alternative
paths, the corresponding neuronal populations in the HC
spike one after another  \citep{johnson2007neural}.
Such neuronal patterns in the HC appear to directly indicate upcoming behavior,
such as in planning navigational trajectories
\citep{pfeiffer2013hippocampal} and
memory consolidation of choice relevance \citep{lavilleon2015}.
Congruently,
London taxi drivers, humans with high performance in forecasting spatial navigation,
were shown to exhibit increased gray-matter volume in the
HC \citep{maguire2000navigation}.
